Paper Visualization

### 2024-09-02 Scripts - Data Cleaning and Visuals/New Webpage Visualizations.Rmd
made changes

```{python Python Load Libraries, Directories, and Datasets, eval=FALSE, include=FALSE}
import os
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
import numpy as np
import plotly.express as px
import plotly.graph_objects as go
import networkx as nx
import scipy

# Define directories
output_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/"
threads_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Threads/"
comments_directory = "/Users/emerson/Github/usenet_AIDs_discourses_webpage/CSV Files/Comments/"

# Load the datasets with the correct file paths
all_threads = pd.read_csv(os.path.join(threads_directory, "aids_related_threads_82TO86.csv"))
all_comments = pd.read_csv(os.path.join(comments_directory, "aids_related_comments_82TO86.csv"))
```

@@

# Correctly construct the output file path
output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_aids_relevancy_filtered.html")

# Ensure the directory exists
dir.create(dirname(output_file_path), recursive = TRUE, showWarnings = FALSE)

# Use the constructed path for saving the file
tab_df(keywords_summary_df, file = output_file_path)
```

@@

# Save the gt table to an HTML file
output_file_path <- file.path(output_directory, "images and tables", "table_top_terms_and_betas_(all_authors).html")
gtsave(gt_table, output_file_path)
```

@@

# Step 1: Calculate Term Frequencies and Filter for Top Terms
co_occurrence <- crossprod(as.matrix(dtm)) # Create co-occurrence matrix
# Set a threshold to filter less relevant terms based on frequency
term_frequency <- rowSums(co_occurrence) # Calculate term frequency
threshold <- quantile(term_frequency, 0.75) # Set threshold for top 25% most frequent terms
filtered_terms <- which(term_frequency > threshold)
filtered_co_occurrence <- co_occurrence[filtered_terms, filtered_terms]

@@

# Save the plot to a PNG file with increased size
ggsave(file.path(output_directory, "images and tables", "plot_co-occurrence_network.png"), 
       plot = co_occurrence_plot, width = 20, height = 16, dpi = 300)  # Increased dimensions
```

```{r Interactive Co-occurrence Network with Plotly, eval=TRUE, include=TRUE}
# Load necessary library
library("threejs")

# Prepare data for 3D network
# We will use the filtered_co_occurrence and term_topic_df from the previous code block

# Create an igraph object from the filtered co-occurrence matrix
graph_3d <- graph_from_adjacency_matrix(filtered_co_occurrence, weighted = TRUE, mode = "undirected", diag = FALSE)

# Simplify the graph to avoid self-loops and redundant edges
graph_3d <- simplify(graph_3d)

# Prepare colors based on topic assignment
topic_colors <- RColorBrewer::brewer.pal(6, "Set1")[term_topic_df$topic]

# Create the 3D force-directed network
network_3d <- graphjs(
  graph_3d,
  vertex.size = log1p(term_frequency[filtered_terms]),
  vertex.label = V(graph_3d)$name,
  vertex.color = topic_colors,
  edge.width = E(graph_3d)$weight / max(E(graph_3d)$weight) * 5,  # Scale edge width
  main = "Interactive 3D Co-occurrence Network of Key Themes in AIDS Discussion"
)

# Save the interactive 3D network to an HTML file
htmlwidgets::saveWidget(network_3d, file = file.path(output_directory, "images and tables/new web visualizations", "interactive_plot_3d_cooccurrence_network.html"))
```

@@

output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_influential_authors.html")
tab_df(influential_authors_metadata_with_totals, file = output_file_path)
```

@@

# Correctly construct the output file path
output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_sentiment_scores_combined.html")

@@

# Display the combined descriptive statistics table using sjPlot
tab_df(
  combined_sentiment_stats,
  title = "Descriptive Statistics for Sentiment Scores of Different Datasets",
  show.rownames = FALSE,
  show.ci = FALSE,
  show.p = FALSE,
  digits = 2,
  file = output_file_path)
```

@@

# Save the plot to a PNG file
output_file_path <- file.path(output_directory, "images and tables", "plot_time_series_sentiment_line_graph.png")
ggsave(output_file_path, plot = time_series_plot, width = 10, height = 6, dpi = 300)
```

@@

# Save the gt table to an HTML file
output_file_path <- file.path(output_directory, "images and tables", "table_top_terms_and_betas_(influential_authors).html")
gtsave(gt_table, output_file_path)
```

@@

output_file_path <- file.path(output_directory, "images and tables", "table_topic_matches.html")

tab_df(best_matches, ,
  file = output_file_path)

@@

output_file_path_transposed <- file.path(output_directory, "images and tables", "table_topic_matches_transposed.html")
tab_df(transposed_best_matches,
  file = output_file_path_transposed)
```

@@

ggsave(file.path(output_directory, "images and tables", "plot_topic_influence_comparison_bar_graph.png"), 
       width = 10, height = 6, dpi = 300)
```

@@

# Save the plot with a higher DPI for better clarity
output_file_path <- file.path(output_directory, "images and tables", "plot_topic_prevalence_line_graph.png")
ggsave(output_file_path, plot = line_plot, width = 12, height = 8, dpi = 300)
```

@@

# Save the plot to a file
output_file_path <- file.path(output_directory, "images and tables/plot_top_15_most_active_users_by_newsgroup.png")
ggsave(output_file_path, plot = bar_plot, width = 10, height = 6, dpi = 300)
```
```{r Thematic evolution}
library(tidytext)
library(tidyverse)

@@

# Save the plot
output_file_path <- file.path(output_directory, "images and tables", "plot_keyword_adoption_over_time.png")
ggsave(output_file_path, plot = keyword_adoption_plot, width = 16, height = 10, dpi = 300)
```

@@

# Save the plot
output_file_path <- file.path(output_directory, "images and tables", "plot_influence_propagation_network_improved.png")
ggsave(output_file_path, plot = influence_plot, width = 20, height = 16, dpi = 300)
```

>>>>

@@

# Correctly construct the output file path
# output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_aids_relevancy_filtered.html")

# Ensure the directory exists
# dir.create(dirname(output_file_path), recursive = TRUE, showWarnings = FALSE)

# Use the constructed path for saving the file
# tab_df(keywords_summary_df, file = output_file_path)
```

@@

# Save the gt table to an HTML file
# output_file_path <- file.path(output_directory, "images and tables", "table_top_terms_and_betas_(all_authors).html")
# gtsave(gt_table, output_file_path)
```

@@

# Step 1: Calculate Term Frequencies and Filter for Top Terms
co_occurrence <- crossprod(as.matrix(dtm)) # Create co-occurrence matrix

binary_dtm <- as.matrix(dtm)
binary_dtm[binary_dtm > 0] <- 1  # Convert counts to 1s

# Step 2: Calculate document frequency for each term
term_frequency <- colSums(binary_dtm)

# Set a threshold to filter less relevant terms based on frequency
threshold <- quantile(term_frequency, 0.75) # Set threshold for top 25% most frequent terms
filtered_terms <- which(term_frequency > threshold)
filtered_co_occurrence <- co_occurrence[filtered_terms, filtered_terms]

@@

# Save the plot to a PNG file with increased size
# ggsave(file.path(output_directory, "images and tables", "plot_co-occurrence_network.png"), 
#       plot = co_occurrence_plot, width = 20, height = 16, dpi = 300)  # Increased dimensions
```

@@

# output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_influential_authors.html")
# tab_df(influential_authors_metadata_with_totals, file = output_file_path)
```

@@

# Correctly construct the output file path
# output_file_path <- file.path(output_directory, "images and tables", "table_descriptive_statistics_sentiment_scores_combined.html")

@@

# Display the combined descriptive statistics table using sjPlot
# tab_df(
  #combined_sentiment_stats,
  #title = "Descriptive Statistics for Sentiment Scores of Different Datasets",
  #show.rownames = FALSE,
  #show.ci = FALSE,
  #show.p = FALSE,
  #digits = 2,
  #file = output_file_path)
```

@@

# Save the plot to a PNG file
# output_file_path <- file.path(output_directory, "images and tables", "plot_time_series_sentiment_line_graph.png")
# ggsave(output_file_path, plot = time_series_plot, width = 10, height = 6, dpi = 300)
```

@@

# Save the gt table to an HTML file
# output_file_path <- file.path(output_directory, "images and tables", "table_top_terms_and_betas_(influential_authors).html")
# gtsave(gt_table, output_file_path)
```

@@

#output_file_path <- file.path(output_directory, "images and tables", "table_topic_matches.html")

#tab_df(best_matches, ,
 #file = output_file_path)

@@

# output_file_path_transposed <- file.path(output_directory, "images and tables", "table_topic_matches_transposed.html")
# tab_df(transposed_best_matches, file = output_file_path_transposed)
```

@@

# ggsave(file.path(output_directory, "images and tables", "plot_topic_influence_comparison_bar_graph.png"), width = 10, height = 6, dpi = 300)
```

@@

# Save the plot with a higher DPI for better clarity
# output_file_path <- file.path(output_directory, "images and tables", "plot_topic_prevalence_line_graph.png")
# ggsave(output_file_path, plot = line_plot, width = 12, height = 8, dpi = 300)
```

@@

# Save the plot to a file
# output_file_path <- file.path(output_directory, "images and tables/plot_top_15_most_active_users_by_newsgroup.png")
# ggsave(output_file_path, plot = bar_plot, width = 10, height = 6, dpi = 300)
```

```{r Thematic evolution}
library(tidytext)
library(tidyverse)

@@

# Save the plot
# output_file_path <- file.path(output_directory, "images and tables", "plot_keyword_adoption_over_time.png")
# ggsave(output_file_path, plot = keyword_adoption_plot, width = 16, height = 10, dpi = 300)
```

@@

# Save the plot
# output_file_path <- file.path(output_directory, "images and tables", "plot_influence_propagation_network_improved.png")
# ggsave(output_file_path, plot = influence_plot, width = 20, height = 16, dpi = 300)
```

### 2024-09-02 Scripts - Data Cleaning and Visuals/Paper Visualizations.Rmd
made changes

# Create the improved plot with simplified legend
co_occurrence_plot <- ggplot(graph_layout, aes(x = x, y = y)) +
  geom_edge_link(aes(edge_alpha = weight), edge_width = 0.3, color = "gray70", alpha = 0.3) +
  geom_node_point(aes(size = log1p(term_frequency[filtered_terms]), color = term_topic_df$topic_name), show.legend = TRUE, alpha = 0.8) +
  geom_text_repel(aes(label = name), 
                  max.overlaps = 20,
                  force = 10,
                  point.padding = 0.5,
                  segment.color = "gray50",
                  min.segment.length = 0,
                  box.padding = 0.7,
                  segment.size = 0.2,
                  size = 8) +
  geom_mark_hull(aes(group = term_topic_df$topic_name, fill = term_topic_df$topic_name), 
                 alpha = 0.1, show.legend = FALSE) +
  scale_size(range = c(2, 12), name = "Term Frequency") +
  scale_color_brewer(palette = "Set1", name = "Topic") +
  scale_fill_brewer(palette = "Set1", guide = "none") +  # Remove fill from legend
  coord_cartesian(xlim = c(-8, 8), ylim = c(-8, 8)) +
  theme_void(base_size = 16) +
  theme(
    aspect.ratio = 1,
    legend.position = "right",
    legend.box = "vertical",
    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
    plot.margin = margin(40, 40, 40, 40),
    plot.background = element_rect(fill = "white", color = NA),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 12)
  ) +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  labs(title = "Co-occurrence Network of Key Themes in AIDS Discussion",
       caption = "Node size represents term frequency. Colors indicate topics identified by LDA.")

@@

# Save the plot
output_file_path <- file.path(output_directory, "images and tables", "plot_influence_propagation_network_improved.png")
ggsave(output_file_path, plot = influence_plot, width = 20, height = 16, dpi = 300)
```

>>>>

# Create the improved plot with simplified legend
co_occurrence_plot <- ggplot(graph_layout, aes(x = x, y = y)) +
  geom_edge_link(aes(edge_alpha = weight), edge_width = 0.3, color = "gray70", alpha = 0.3) +
  geom_node_point(aes(size = log1p(term_frequency[filtered_terms]), color = term_topic_df$topic_name), show.legend = TRUE, alpha = 0.8) +
  geom_text_repel(aes(label = name), 
                  max.overlaps = 20,
                  force = 10,
                  point.padding = 0.5,
                  segment.color = "gray50",
                  min.segment.length = 0,
                  box.padding = 0.7,
                  segment.size = 0.2,
                  size = 8) +
  geom_mark_hull(aes(group = term_topic_df$topic_name, fill = term_topic_df$topic_name), 
                 alpha = 0.1, show.legend = FALSE) +
  scale_size(range = c(2, 12), name = "Term Frequency") +
  scale_color_brewer(palette = "Set1", name = "Topic") +
  scale_fill_brewer(palette = "Set1", guide = "none") +  # Remove fill from legend
  coord_cartesian(xlim = c(-9, 9), ylim = c(-9, 9)) +
  theme_void(base_size = 16) +
  theme(
    aspect.ratio = 1,
    legend.position = "right",
    legend.box = "vertical",
    plot.title = element_text(hjust = 0.5, size = 18, face = "bold"),
    plot.margin = margin(40, 40, 40, 40),
    plot.background = element_rect(fill = "white", color = NA),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 12)
  ) +
  guides(color = guide_legend(override.aes = list(size = 5))) +
  labs(title = "Co-occurrence Network of Key Themes in AIDS Discussion",
       caption = "Node size represents term frequency. Colors indicate topics identified by LDA.")

@@

# Save the plot
output_file_path <- file.path(output_directory, "images and tables", "plot_influence_propagation_network_improved.png")
ggsave(output_file_path, plot = influence_plot, width = 20, height = 16, dpi = 300)
```
# For Webpage

```{r Interactive Co-Occurance Network of Top Terms, eval=TRUE}
# Load necessary libraries
library(visNetwork)
library(igraph)

library(visNetwork)
library(igraph)

# Create an igraph object from the filtered co-occurrence matrix
graph_3d <- graph_from_adjacency_matrix(filtered_co_occurrence, weighted = TRUE, mode = "undirected", diag = FALSE)

# Simplify the graph to avoid self-loops and redundant edges
graph_3d <- simplify(graph_3d)

# Prepare colors based on topic assignment
topic_colors <- RColorBrewer::brewer.pal(6, "Set1")[term_topic_df$topic]

# Prepare data for visNetwork
nodes <- data.frame(
  id = V(graph_3d)$name,
  label = V(graph_3d)$name,  # Labels are always visible
  group = term_topic_df$topic,  # Group nodes by topic
  value = log1p(term_frequency[filtered_terms]) * 8,  # Increase node size scaling for visibility
  title = paste("<p><b>Node:</b>", V(graph_3d)$name, "<br><b>Frequency:</b>", term_frequency[filtered_terms], "</p>")  # Custom hover popups
)

# Sort nodes alphabetically by label
nodes <- nodes[order(nodes$label), ]

edges <- data.frame(
  from = as.character(ends(graph_3d, E(graph_3d))[, 1]),
  to = as.character(ends(graph_3d, E(graph_3d))[, 2]),
  value = E(graph_3d)$weight / max(E(graph_3d)$weight) * 1,  # Scale edge width for visibility
  label = round(E(graph_3d)$weight, 2)  # Add edge labels
)

network_vis <- visNetwork(nodes, edges, width = "100%", height = "90vh") %>%
  visNodes(
    shape = "dot",
    scaling = list(min = 5, max = 30),
    font = list(size = 35),
    color = list(
      background = topic_colors,
      border = "black",
      highlight = "red"
    ),
    title = nodes$title
  ) %>%
  visEdges(
    width = ~value,
    color = list(color = 'gray', highlight = 'red'),
    smooth = list(enabled = TRUE, type = "continuous", roundness = 1)
  ) %>%
  visOptions(
    highlightNearest = list(enabled = TRUE, hover = TRUE),
    nodesIdSelection = list(enabled = TRUE, useLabels = TRUE, main = "Select by term"),  # Changed label for node selection
    selectedBy = list(variable = "group", sort = TRUE, main = "Select by topic")  # Changed label for group selection
  ) %>%
  visPhysics(
    stabilization = FALSE,
    solver = "barnesHut",
    barnesHut = list(
      gravitationalConstant = -30000,  # Increase negative value for stronger repulsion
      springLength = 500,              # Increase spring length to spread nodes apart
      springConstant = 0.01            # Decrease spring constant for more flexible edges
    )
  ) %>%
  visInteraction(
    dragNodes = TRUE,
    dragView = TRUE,
    zoomView = TRUE,
    navigationButtons = TRUE,  # Adds navigation buttons
    keyboard = TRUE
  ) %>%
  visLayout(
    improvedLayout = TRUE
  )

# Save the network graph to an HTML file with full width and height
network_graph_path <- file.path(output_directory, "images and tables/new web visualizations/interactive_plot_3d_cooccurrence_network.html")
visSave(network_vis, file = network_graph_path)

# Custom title and legend creation in HTML
title_html <- '
<div style="position: absolute; top: 40px; left: 50%; transform: translateX(-50%); font-size: 24px; font-weight: bold; font-family: Arial, sans-serif;">
  Interactive Co-Occurrence Network of Top Terms
</div>
'

legend_html <-'
<div style="position: absolute; top: 40px; right: 40px; background-color: #f0f0f0; border: 1px solid #666; padding: 7px; text-padding: 7px; border-radius: 5px; font-family: Arial, sans-serif;">
  <span style="color: #94df5c;">●</span> Topic 1
  <span style="color: #ffff54;">●</span> Topic 2
  <span style="color: #eb8584;">●</span> Topic 3<br>
  <span style="color: #a787de;">●</span> Topic 4
  <span style="color: #dd82ee;">●</span> Topic 5
  <span style="color: #9fc0f7;">●</span> Topic 6
</div>
'

# Inject the custom title and legend into the HTML file
html_content <- readLines(network_graph_path)
html_content <- c(title_html, html_content, legend_html)
writeLines(html_content, network_graph_path)
```
